\documentclass[12pt, a4paper]{awesome-cv}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

\fontdir[fonts/]
\definecolor{awesome}{HTML}{7851a9}

\definecolor{darktext}{HTML}{414141}
\definecolor{text}{HTML}{0c0c0c}
\definecolor{graytext}{HTML}{1f1f1f}
\definecolor{lighttext}{HTML}{333333}
\definecolor{Royal}{HTML}{7851a9}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\makeatletter
\patchcmd{\@sectioncolor}{\color}{\mdseries\color}{}{}
\makeatother

% Available options: circle|rectangle,edge/noedge,left/right
\name{Michael}{O'Donnell}
\position{job title: Senior Data Scientist} % {\enskip\cdotp\enskip}
\address{Location: Manchester, United Kingdom}

\mobile{(+44) 7712 589981}
\email{michael@eyecatching.co.uk}
% \github{M7641}
\linkedin{mike-o-donnell-715b8574}

\begin{document}
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
\makecvfooter{}{Michael O'Donnell~~~·~~~Résumé}{\thepage}

\cvsection{Summary}
\begin{cvparagraph}

I am a Lead Machine Learning Engineer at UiPath, a Software‑as‑a‑service company, since 2020. Previously, I was a Quantitative Analyst
for the management consultancy Oliver Wyman. My higher education was in Mathematics (MSci) from Lancaster University. I also
did a year abroad at Western University in Ontario, Canada.
\newline \newline
At Peak, I develop and deploy applications powered by Machine Learning (ML) models. I am responsible for end-to-end delivery,
including data engineering, building machine learning models, providing outputs through web applications and APIs, and proving added business value through A/B testing.
I have over seven years of experience in Python, R and multiple dialects of SQL. I'm driven by the desire to improve and optimise business processes continuously.
\end{cvparagraph}


\cvsection{Experience}
\begin{cventries}

\cventry{Lead Machine Learning Engineer}{UiPath}{Manchester Goods Yard, St.John’s, Manchester M3 3GS}{February 2020 - Present}
{\begin{cvitems}
\item {
  My projects have been focused on Customer propensity models, Customer LTV models, Recommendation systems, e‑commerce pricing and markdown optimisation.
  I act as the primary contact for the customer during solution deployment;   hence, I have experience in stakeholder management and presenting to non‑technical audiences,
  including the C‑Suite level.
}
\item{A few projects of mine are:
  \begin{enumerate}
    \item  Developing a solution to explain black‑box machine learning models using SHAP values. The primary use
    case was to advise on financial services product strategy by providing insights into the 17 separate
    customer propensity models that I developed.
    \item Deploying a markdown optimisation tool for a major UK fashion retailer with intense deadlines.
    This solution increased gross margin by 9.4ppt with comparable sell‑through rates, as proven by an A/B test.
    \item  Developing a P\&L application in a month that was used to identify 10 Million pounds of savings
    within a medium‑sized retail business.
    \item  Delivering a recommendation engine used within the CRM D365 to generate 2 Million pounds of additional
    annual revenue for a manufacturing business along side other models such as a Customer LTV model.
  \end{enumerate}
}
\item {The technical skills I use daily are data importing from various sources such as SFTP servers, REST Apis, and AWS's S3.
  Data engineering through DBT on Data Warehouses such as AWS's Redshift and Snowflake. Python is used in developing ML
  models, primarily using TensorFlow. APIs in FastAPI and Dash for Web Applications. The DevOps tools include git for version
  control, docker for containerisation, and pre‑commit hooks for code hygiene. I adopt the best technology
  for the job and continuously look for new ways to boost productivity.
}
\item {Outside of project delivery, I contribute to Peak's core products. I developed the first
  version of our markdown application's front end and contribute React components to our component library. Also, I am
  involved in various initiatives to improve code quality, including creating Python templates. I also help to maintain our internal tooling.}
\item { Finally, I mentor several Data Scientists through coaching, technical support and project guidance.
  This includes revising timelines and identifying risks in the projects for which my team is responsible.}
\end{cvitems}
\vspace{8.0mm}
      \begin{cvsubentries}
        \cvsubentry{}{Lead Machine Learning Engineer}{May 2025 - present}{}
        \cvsubentry{}{Senior Data Scientist}{Janurary 2023 - May 2025}{}
        \cvsubentry{}{Data Scientist}{Februrary 2020 - January 2023}{}
      \end{cvsubentries}
}
\cventry{Financial Services Quantitative Analyst}{Oliver Wyman}{7 New Bridge St W, Newcastle upon Tyne NE1 8AQ}{March-September 2019}
	{\begin{cvitems}
	\item {
My primary responsibility was to develop an ML model to improve the price decision‑making process
of a rental motor insurance product and implement A/B testing to demonstrate efficacy.
		}
	\item {
Another contribution was developing a report communicating key metrics around model performance. I used a
Python implementation of reveal.js to generate an HTML file every week. This saved plenty of time as it avoided
re-creating the report in PowerPoint.
		}
	\end{cvitems}
}
\end{cventries}

\cvsection{Technical Skills}
\begin{cvskills}
\cvskill{Programming Languages:}{Python, R, TypeScript, and Rust. }
\cvskill{SQL Dialects:}{Redshift, PostgreSQL, Apache Impala, MySQL, Snowflake, and using DBT for data pipeline management. }
\cvskill{Model Development Packages:}{Tensorflow, XGBoost, LightGBM, PyMC3, scikit-learn}
\cvskill{Data Processing Packages:}{Pandas, Numpy and Polars in Python. Tidyverse in R}
\cvskill{CD/CI:}{Git, Github actions, Docker, Pre-commit hooks, Pytest}
\cvskill{Data Visualisation:}{Matplotlib, Plotly, Bokeh in Python. ggplot, Plotly R in R. Mantine Charts in TypeScript.}
\cvskill{Web Applications:}{Dash, React with Vite and R Shiny}
\cvskill{API frameworks:}{FastAPI and Axum}
\end{cvskills}

\cvsection{Education}

\begin{cventries}

\cventry{MSci. First Class Honours in Mathematics (Study Abroad)}{Lancaster University}{}{2014 - 2018}{
	\begin{cvitems}
	\item {
I chose courses to establish skills in Probability theory, Stochastic processes, ML and traditional
skills in mathematical rigour and analysis. Other courses include Statistical methods, Reinforcement learning, Mathematical Spaces, Ring Theory, and Stochastic
Calculus with a focus on the derivation of the Black‑Scholes model and Heston model for derivative pricing. Finally,
my dissertation was complex analysis in several variables.
		}
	\item {
		My year abroad was at Western University in Ontario, Canada. It was a great experience to study in a different
		country and learn about the different teaching styles and cultures. Working abroad is something I would do in the future.
	}
	\end{cvitems}
}

\cventry{A-Levels}{Calderstones School}{}{2012-2014}{
  Mathematics: A*, \space Physics: B, \space Further Mathematics: B.
}

\cventry{GCSEs}{Calderstones School}{}{2010-2012}{
  Mathematics: A, English Language: C, 8 other GCSEs with grades A-C, 2 OCR Awards in IT, and a BTEC in sport.
}

\end{cventries}

\end{document}
